---
title: 'Chart Remake - Google Trends: Hangover Cure'
output:
  html_document:
    code_folding: hide
    df_print: paged
  pdf_document: default
---

This is a remake of chartr.co plot using tidyverse. The plot shows the google trend for "Hangover Cure" searches over a period of 90 days.


```{r echo=FALSE}
library(tidyverse)
```

# Data 💰
We start by loading the data and printing first few rows.

```{r}
df <- read_csv("../data/us-90days.csv")
head(df, 3)
```

Print some basic stats about our data.

```{r}
summary(df)
```

We are going to rename the columns to make it easier to reference them. And while we are at it, we will add weekday column that represents day of the week.
```{r}
df <- df %>%
  rename("Count"="hangover cure: (United States)") %>%
  mutate("weekday"=weekdays(Day))

```


# Plot 📈

We now everything we need to plot the data. Let us create the line chart and add other things on top of it.

```{r}
library(ggplot2)
plt <- ggplot(df, aes(Day, Count)) + 
  geom_line() +
  scale_x_date(date_breaks = "weeks", date_labels = "%b-%d") +
  labs(title = "Data is beautiful. Hangovers are not", x="", y="Google Search Volume (Indexed, 100 = Maximum)") + 
  theme(axis.text.x = element_text(angle=45, hjust=1), panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        panel.background = element_blank(), axis.line = element_line(colour = "darkgray")
        )

plt
```

Next, We need to add the vertical lines to highlight the weekends.

```{r}
plt <- plt + geom_vline(aes(xintercept=Day), 
                 data=df %>% filter(weekday %in% c("Saturday", "Sunday")), color="gray", 
                 alpha=0.3, size=2.3)
plt
```

Notice the huge spike around 6th of July - something to do with the long weeked, eh.

Now, all that is left is the annotation. and while we are at it, let's center the title and add subtitle.

```{r}
weekends_df <- df %>% filter(weekday %in% c("Saturday", "Sunday"))
plt + annotate(geom = "text", x=weekends_df$Day[6], y=8, label="Saturday & Sunday", color="darkblue", size=2) + 
  labs(title="Data is Beautiful. Hangovers Are Not", subtitle = "[Google Search Volume for \"hangover cure\"]") +
  theme(plot.title = element_text(size=20, colour = "darkblue", hjust = 0.4),
        plot.subtitle = element_text(size=10, colour = "black", hjust = 0.4))
```

And that's it folks😎.